% University of Strathclyde
% Research dissertation template
% for degrees from the Mechanical & Aerospace Engineering
%------------------------------------------------
\documentclass[a4paper,oneside,12pt]{book}

% fonts
\usepackage{times} 
\usepackage{amsbsy, amsmath, amsfonts}
\usepackage{siunitx}
\usepackage{graphicx}

% text sub- and superscripts
\newcommand{\spr}[1]{\ensuremath{^\textrm{#1}}}
\newcommand{\sub}[1]{\ensuremath{_\textrm{#1}}}

% better tables
\usepackage{multirow}
\usepackage{booktabs}

% links
\usepackage{color}
\usepackage[]{hyperref}
\usepackage{enumitem} % better lists

% Use for bibliography style, Harvard or Vancouver, etc.
\usepackage{natbib}

% figures and tables
\usepackage{caption}
\captionsetup[figure]{labelfont=it,textfont=it}
\captionsetup[table]{labelfont=it,textfont=it}
\usepackage{subfig}

\usepackage[strict]{changepage}

% Redefine \eqref to include Eq. prefix
\makeatletter
\def\tagform@#1{\maketag@@@{(\ignorespaces#1\unskip\@@italiccorr)}}
\makeatother
\let\originaleqref=\eqref
\renewcommand{\eqref}{Eq.~\originaleqref}

% Define margins
\usepackage[left=2.5cm,right=2.5cm,top=2cm,bottom=4cm,includehead,includefoot,headheight=15pt]{geometry}

% Page headers
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % optional
%\fancyhead[L]{\nouppercase{\leftmark} \hfill Section \nouppercase{\rightmark}}
\fancyhead[L]{\nouppercase{\leftmark}}
\cfoot{\thepage}
\pagestyle{fancy}

% Line spacing
%\def\baselinestretch{1.5} 
\usepackage{setspace}
\setstretch{1.5}

% Defines strath-specific title page
\usepackage{strathtitle}

% Nomenclature
\usepackage{nomencl}
\makenomenclature

\usepackage{etoolbox}  % option to group symbols
\renewcommand\nomgroup[1]{%
  \item[\bfseries
  \ifstrequal{#1}{C}{Constants}{%
  \ifstrequal{#1}{S}{Variables}{}}%
]}

%-------------------------------------------
\begin{document}

% Complete with your own details
\author{Carnicero}
\title{Dynamic Line Rating without field devices}
\course{MSc Smart Grids}
\supervisor{Dr Varela}

\maketitle

\frontmatter

% Declaration
\chapter*{Copyright Declaration}
This thesis is the result of the author's original research. It has been composed by the author and has not been previously submitted for examination which has led to the award of a degree. 

The copyright of this thesis belongs to the author under the terms of the United Kingdom Copyright Acts as qualified by University of Strathclyde Regulation 3.50. Due acknowledgement must always be made of the use of any material contained in, or derived from, this thesis. 
\vspace{1cm}

\noindent Signed: \\
\noindent Date: \today

% Declaration
\chapter*{Abstract}
Abstract should be on one page. It should summarise the project objectives, the work carried out, methods used, the main research findings arising from the work and conclusions reached. 

\chapter*{Acknowledgements}
This thesis is the result of the author’s original research. However if any external support, help or contributions were received, it must be acknowledged here. 

\tableofcontents

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\addcontentsline{toc}{chapter}{Nomenclature}
\mbox{}
\nomenclature[C]{$c$}{Speed of light in a vacuum, \SI{299792458}{m/s}}
\nomenclature[C]{$h$}{Plank's constant, \SI{6.62607004e-34}{m^2.kg/s}} %m\spr{2}kg/s
\nomenclature[S]{$g$}{Gravitational acceleration, m/s\spr{2}}
\nomenclature[S]{$\mathbf{q}$}{Quaternions}
\nomenclature[S]{$V$}{Volume, m\spr{3}}
\nomenclature[S]{$\rho$}{Density, kg/m\spr{3}}

\printnomenclature

%-------------------------------------------------
\mainmatter

\input{chapters/01_introduction}
\input{chapters/02_description_of_technologies}
\input{chapters/03_state_of_the_art}
\input{chapters/04_definition_of_the_work}
\input{chapters/05_system_model_developed}
\input{chapters/06_analysis_of_results}
\input{chapters/07_conclusions}

\addcontentsline{toc}{chapter}{References}
\renewcommand{\bibname}{References}
\bibliographystyle{agsm} % Harvard style
\bibliography{myrefs} 

%-----------------------------
\appendix
\input{chapters/08_appendix}

\end{document}
